\begin{thebibliography}{99}

\bibitem{Tropper2006}{A.~C.~Tropper, S.~Hoogland,
\textit{Review, Extended cavity surface-emitting semiconductor lasers},
Progress in Quantum Electronics 30, 1--43, (2006)}

\bibitem{Ranta2014OptLett}{A.~Rantam\"aki et al.,
\textit{High-power flip-chip semiconductor disk laser
in the 1.3 $\mu$m wavelength band},
Optics Letters, Vol. 39, No. 16, (2014)}

\bibitem{Kemp2008}{A.~J.~Kemp et al.,
\textit{Thermal Management in 2.3-$\mu$m Semiconductor Disk
Lasers: A Finite Element Analysis},
IEEE Journal of Quantum Electronics, Vol. 44, No. 2, (2008)}

\bibitem{Chernikov2010}{A.~Chernikov et al.,
\textit{Influence of the spatial pump distribution on
the performance of high power vertical-external-cavity surface-emitting
lasers},
Appl. Phys. Lett., vol. 97, no. 19, pp. 191110-1-191110-3, 2010}

\bibitem{Calvez2009}{S.~Calvez et al.,
\textit{Semiconductor disk lasers for the generation of visible and
ultraviolet radiation},
Laser \& Photon. Rev. 3, No. 5, 407--434 (2009)}

\bibitem{Sirbu2014OptExp}{A.~Sirbu et al., 
\textit{High performance wafer-fused semiconductor disk lasers
emitting in the 1300 nm waveband},
Optics Express, Vol. 22, Issue 24, pp. 29398-29403 (2014)}

\bibitem{Baili2009}{G.~Baili et al.,
\textit{Experimental demonstration of
a tunable dual-frequency semiconductor laser
free of relaxation oscillations},
Optics Letters, Vol. 34, No. 21, (2009)}

\bibitem{Lukowski2015}{M.~Lukowski et al.,
\textit{Widely Tunable High-Power Two-Color VECSELs
for New Wavelength Generation},
IEEE Journal of Selected Topics in Quantum Electronics,
Vol. 21, No. 1, (2015)}

\bibitem{Bedford2005}{R.~G.~Bedford et al.,
\textit{Power-limiting mechanisms in VECSELs}
in Proc. Enabling Photon. Technol.
Defense Security Aerospace Appl., (2005)}

\bibitem{Sirbu2014SPIE}{A.~Sirbu et al., 
\textit{Wafer-fused VECSELs emitting in the 1310 nm waveband},
Proc. SPIE 8966, 8966OG-1-8 (2014)}

\bibitem{Hader2011}{J.~Hader et al.,
\textit{VECSEL optimization using microscopic many-body physics},
IEEE J. Sel. Top. Quantum. Electron. 17, 1753 (2011)}

\bibitem{Kemp2005}{A.~J.~Kemp et al.,
\textit{Thermal Management in Vertical-External-Cavity
Surface-Emitting Lasers: Finite-Element
Analysis of a Heatspreader Approach},
IEEE Journal of Quantum Electronics, Vol. 41, No. 2, (2005)}

\bibitem{Heinen2012el}{B.~Heinen et al.,
\textit{106~W continuous-wave output power
from vertical-external-cavity surface-emitting laser},
Electron. Lett. 48, 516 (2012)}

\bibitem{Vetter2012}{S.~L.~Vetter, S.~C.~Calvez,
\textit{Thermal Management of Near-Infrared
Semiconductor Disk Lasers With AlGaAs Mirrors
and Lattice (Mis)Matched Active Regions},
IEEE Journal of Quantum Electronics, Vol. 48, No. 3, (2012)}

\bibitem{Devautour2013}{M.~Devautour et al., 
\textit{Thermal Management for High-Power Single-Frequency
Tunable Diode-Pumped VECSEL Emitting in the Near- and Mid-IR},
IEEE J. of Sel. Topics in Quant. El., Vol. 19, No. 4, (2013)}

\bibitem{Heinen2012}{B.~Heinen et al.,
\textit{On the Measurement of the Thermal Resistance
of Vertical-External-Cavity Surface-Emitting
Lasers (VECSELs)},
IEEE J. Quantum Electron. 48, 934 (2012)}

\bibitem{Giet2008}{S.~Giet et al.,
\textit{Comparison of thermal management techniques
for semiconductor disk lasers},
Proc. of SPIE Vol. 6871, 687115, (2008)}

\bibitem{Hader2013}{J.~Hader et al.,
\textit{On the measurement of the thermal impedance
in vertical-external-cavity surface-emitting lasers}
Journal of Applied Physics 113, 153102 (2013)}

\bibitem{Lindberg2005}{H.~Lindberg et al.,
\textit{Thermal Management of Optically Pumped
Long-Wavelength InP-Based Semiconductor
Disk Lasers},
IEEE Journal of Selected Topics in Quantum Electronics, Vol. 11, No. 5, (2005)}

\bibitem{Le1991}{H.~Q.~Le et al.,
\textit{Scalable high-power optically pumped GaAs laser}
App. Phy. Lett. 58, pp. 1967--1969, (1991)}

\bibitem{Korpi2010}{V.-M.~Korpij\"arvi et al.,
\textit{11 W single gain-chip dilute nitride disk laser
emitting around 1180 nm},
Optics Express, Vol. 18, No. 25, (2010)}

\bibitem{Nakwaski1992}{W.~Nakwaski and M.~Osinski,
\textit{Thermal resistance of top-surface-emitting vertical-cavity
semiconductor lasers and monolithic two-dimensional arrays}
Electronics Letters, 28(6), 72-574, (1992)}

\bibitem{ThorlabsAC}{Thorlabs,
\textit{Achromatic Doublets},\\
http://www.thorlabs.de/NewGroupPage9.cfm?ObjectGroup\_ID=259}

\bibitem{ThorlabsPM}{Thorlabs,
\textit{Power meter operation manual},\\
http://www.thorlabs.de/thorcat/19500/PM100USB-Manual.pdf}

\bibitem{Barlow}{R.~J.~Barlow,
\textit{Statistics -- A guide to the use of statistical methods
in the physical sciences},
The Manchester Physics Series,
Wiley, (1999)}

\bibitem{Efron1983}{B.~Efron, G.~Gong,
\textit{A Leisurely Look at the Bootstrap, the Jackknife and Cross-Validation},
The American Statistician, Vol 37, No 1 (Feb 1983), pp. 36-48}

\bibitem{Hessenius2011}{C.~Hessenius et al.,
\textit{Lateral lasing and ASE reduction in VECSELs},
in Proc. Vertical External Cavity Surface Emitting Lasers,
San Francisco, CA, 2011, pp. 791909-1-791909-8}

\bibitem{Chernikov2011}{A.~Chernikov et al.,
\textit{Heat management in high-power vertical-external-cavity
surface-emitting lasers},
IEEE J. Sel. Topics Quantum Electron., vol. 17,
no. 6, pp. 1772-1778, Nov.-Dec. 2011}

\bibitem{Mansell2000}{J.~D.~Mansell et al.,
\textit{Gaussian to Super-Gaussian Intensity Profile
Conversion with Refractive Micro-Optics},
online http://www.mansellassociates.com/CLEOTalk.pdf, (2000)}

\bibitem{Epperlein1993}{P.~W.~Epperlein,
\textit{Micro-temperature measurements on semiconductor laser
mirrors by reflectance modulation:
a newly developed technique for laser characterization},
Jpn.~J.~Appl.~Phys.~32, 5514-5522, (1993)}

\bibitem{Pierscinski2009}{K.~Pierscinski et al.,
\textit{Investigation of thermal management in optically pumped,
antimonide VECSELs},
Microelectron.~J., vol. 40, no. 3, pp. 558-561, (2009)}

\bibitem{Tessier2001}{G.~Tessier et al.,
\textit{Quantitative thermal imaging by synchronous
thermoreflectance with optimized illumination wavelengths},
Appl.~Phys.~Lett.~78, 2267-071106, (2001)}

\bibitem{SpringerMat}{Springer Materials,
\textit{The Landolt-B\"ornstein Database},
online http://www.springermaterials.com}

\bibitem{QE}{U.~Keller,
\textit{Lecture Quantum Electronics}, ETH Zurich, (2012)}

\bibitem{Edmund}{Edmund optics,
\textit{Understanding Spatial Filters},
online http://www.edmundoptics.de/technical-resources-center/lasers/understanding-spatial-filters}

\bibitem{Newport}{Newport,
\textit{Spatial Filters},
online http://www.newport.com/Spatial-Filters/144910/1033/content.aspx}

\bibitem{Thorlabs}{Thorlabs,
\textit{Principles of Spatial Filters},\\
http://www.thorlabs.de/NewGroupPage9.cfm?ObjectGroup\_ID=997}

\bibitem{Osinski1993}{M.~Osinski et al.,
\textit{Effective thermal conductivity analysis of
1.55 $\mu$m InGaAsP/InP vertical-cavity top-surface-emitting microlasers},
Electron. Lett., vol. 29, issue 11, (1993)}

\bibitem{ioffe}{Electronic Archive,
\textit{New Semiconductor Materials, Characteristics and
Properties},
online http://www.ioffe.ru/SVA/NSM/}

\bibitem{Piprek1998}{J.~Piprek et al.,
\textit{Thermal Conductivity Reduction in GaAs-AlAs
Distributed Bragg Reflectors},
IEEE Photonics Technology Letters, VOL. 10, NO. 1, (1998)}

\bibitem{Ranta2014APL}{A.~Rantam\"aki et al.,
\textit{High power semiconductor disk laser with a
semiconductor-dielectric-metal compound mirror},
Appl. Phys. Lett. 104, (2014)}







\bibitem{Piprek2002}{J.~Piprek et al.,
\textit{What Limits the Maximum Output Power of
Long-Wavelength AlGaInAs/InP Laser Diodes?},
IEEE Journal of Quantum Electronics, VOL. 38, NO. 9, (2002)}





\bibitem{Schubert}{E.~F.~Schubert,
\textit{Materials - Refractive index and extinction coefficient},
online http://homepages.rpi.edu/~schubert/Educational-resources/Materials-Refractive-index-and-extinction-coefficient.pdf,
Rensselaer Polytechnic Institute, NY USA}


\end{thebibliography}